\chapter{Acknowledgement}

We would like to extend our sincere gratitude to Associate Professor Tran Minh Triet and M.Sc. Do Trong Le for their dedicated guidance and continuous support throughout our undergraduate studies. Their mentorship has been instrumental in nurturing our academic development and inspiring us to pursue research with curiosity and determination. Their encouragement and valuable advice have accompanied us through every stage of this thesis.

We are especially thankful to Dr. Dao Thi Phuong Thao for her generous support in providing essential medical data and professional healthcare knowledge, which have been crucial to the successful execution of our project. Her expertise has greatly enriched our understanding of the medical domain and helped us apply our research in a meaningful and practical context.

Our appreciation also goes to all the lecturers of the Faculty of Information Technology, University of Science, VNU-HCM, whose outstanding teaching and dedication to academic excellence have laid a strong foundation for our studies. Their insightful lectures and guidance have equipped us with the necessary knowledge and skills for academic and research success.

We are grateful to our friends for their constant support, constructive feedback, and enthusiastic encouragement, all of which have made this challenging journey more enjoyable and rewarding. Their contributions have helped improve the quality of our work in many ways.

Our special thanks also go to the Software Engineering Laboratory (SELab), University of Science, VNU-HCM, for providing excellent research facilities and technical assistance that enabled us to successfully complete our thesis.

Finally, we are deeply indebted to our families for their unconditional love, patience, and endless encouragement. Their support has been a pillar of strength, allowing us to overcome difficulties and remain focused on achieving our academic goals with confidence and determination.