\section{Demo Plan}
\subsection{Metadata Auto Extraction with Q\&A Pairs Generation}
\begin{itemize}
    \item \textbf{Step 1: Input}
    \begin{itemize}
        \item \textbf{Action:} Input a full description of SeLab into the input box, along with the exact position.
        \item \textbf{Expected Result:} No immediate output is generated.
    \end{itemize}
    
    \item \textbf{Step 2: Q\&A Pair Generation}
    \begin{itemize}
        \item \textbf{Action:} Click the \emph{Generate} button.
        \item \textbf{Expected Result:} The app displays a generating process (from 0--100\%). Once complete, a new screen presents the generated Q\&A pairs.
    \end{itemize}
    
    \item \textbf{Step 3: Regeneration}
    \begin{itemize}
        \item \textbf{Action:} Click the \emph{Regenerate} button.
        \item \textbf{Expected Result:} The app displays the generating process again. A new screen shows a slightly different set of Q\&A pairs when finished.
    \end{itemize}
    
    \item \textbf{Step 4: Submission}
    \begin{itemize}
        \item \textbf{Action:} Click the \emph{Submit} button.
        \item \textbf{Expected Result:} The app shows the submission process (from 0--100\%), and upon completion, notifies the user that the metadata has been successfully updated to the remote database.
    \end{itemize}
\end{itemize}

\subsection{Indoor Space -- Floor 7th and 8th}
\begin{itemize}
    \item \textbf{Step 1: Initiate AR Session}
    \begin{itemize}
        \item \textbf{Action:} Scan the QR code located on the 8th floor.
        \item \textbf{Expected Result:} The system automatically launches the AR camera session.
    \end{itemize}
    
    \item \textbf{Step 2: Location Tracking}
    \begin{itemize}
        \item \textbf{Action:} Walk between the 7th and 8th floors and move the camera into unknown locations.
        \item \textbf{Expected Result:} The system updates and notifies the current location as the user moves between floors and warns when entering undetected environments.
    \end{itemize}
    
    \item \textbf{Step 3: Activate AI Assistance}
    \begin{itemize}
        \item \textbf{Action:} Greet the AI assistant.
        \item \textbf{Expected Result:} The AI assistant responds with guidance on how to query for a destination.
    \end{itemize}
    
    \item \textbf{Step 4: Query to I77}
    \begin{itemize}
        \item \textbf{Action:} Query “Find the path to the I77 room.”
        \item \textbf{Expected Result:} The system displays a clear navigation path leading to the I77 room.
    \end{itemize}
    
    \item \textbf{Step 5: Follow the Navigation Path}
    \begin{itemize}
        \item \textbf{Action:} Walk following the on-screen arrows.
        \item \textbf{Expected Result:} Upon arrival at the I77 room, the system notifies the user that they have reached the destination.
    \end{itemize}
    
    \item \textbf{Step 6: Query for the Research Room}
    \begin{itemize}
        \item \textbf{Action:} Query “How do I get to the research room?”
        \item \textbf{Expected Result:} The system responds with an ambiguity alert, indicating that multiple rooms could match the query (e.g., I87 and I77) and requests more information.
    \end{itemize}
    
    \item \textbf{Step 7: Clarify Destination for Software Engineering}
    \begin{itemize}
        \item \textbf{Action:} Query more specifically “Show path to the room for researching about Software Engineering.”
        \item \textbf{Expected Result:} The system displays the navigation path to the I87 room.
    \end{itemize}
    
    \item \textbf{Step 8: Query for a Room on Floor 8}
    \begin{itemize}
        \item \textbf{Action:} Query “Find the path to the room on floor 8.”
        \item \textbf{Expected Result:} The system again flags the query as ambiguous, indicating that multiple rooms could match the query (e.g., I87 and the restroom on floor 8) and requests more information..
    \end{itemize}
    
    \item \textbf{Step 9: Specify Research Room on Floor 8}
    \begin{itemize}
        \item \textbf{Action:} Combine the vague details by querying “Show me the path to the room for research on floor 8.”
        \item \textbf{Expected Result:} The system correctly displays the navigation path to the I87 room.
    \end{itemize}
\end{itemize}

\subsection{Semi-outdoor Space -- Front Campus of HCMUS}
\begin{itemize}
    \item \textbf{Step 1: Initiate AR Session}
    \begin{itemize}
        \item \textbf{Action:} Scan the QR code at the front gate.
        \item \textbf{Expected Result:} The AR camera session is activated, launching the AR interface in the semi-outdoor environment.
    \end{itemize}
    
    \item \textbf{Step 2: Verify AR Tracking}
    \begin{itemize}
        \item \textbf{Action:} Pan and move the camera around the area.
        \item \textbf{Expected Result:} The system confirms continuous tracking and reliable environment detection.
    \end{itemize}
    
    \item \textbf{Step 3: Query for the Ground Elevator}
    \begin{itemize}
        \item \textbf{Action:} Query “Find the path to the ground elevator of building I.”
        \item \textbf{Expected Result:} The system displays a clear navigation path leading to the ground elevator.
    \end{itemize}
    
    \item \textbf{Step 4: Follow the Navigation Path}
    \begin{itemize}
        \item \textbf{Action:} Walk following the on-screen arrows.
        \item \textbf{Expected Result:} The user arrives at the ground elevator of building I.
    \end{itemize}
    
    \item \textbf{Step 5: Query for the Parking Lot}
    \begin{itemize}
        \item \textbf{Action:} Query “Find the path to the parking lot.”
        \item \textbf{Expected Result:} The system flags the query as ambiguous due to multiple parking lots, requesting additional clarification.
    \end{itemize}
    
    \item \textbf{Step 6: Specify the Underground Parking Lot}
    \begin{itemize}
        \item \textbf{Action:} Query “Show me the path to the underground parking lot.”
        \item \textbf{Expected Result:} The system displays a clear navigation route to the underground parking lot.
    \end{itemize}
\end{itemize}
